---
title: "Exercise 7"
author: "Cameron Bale"
format: docx
---

Kroger is specifically interested in whether their spend on promotions (`Any_Promo_Spend`) and discounts (`Price_Decr_Spend`) is driving their sales (`Sales`) in the soup category. Do the following:

1. Import the soup data and the `tidyverse` and `tidymodels` libraries.
2. Create a regression model and fit it to the appropriate variables.
3. Examine the coefficients - do promotional spend and price decreases appear to have a positive or negative effect on sales?
4. Render the Quarto document into Word and upload to Canvas.

**Five points total, one point for:**

- **Importing the libraries and data.**

**Two points each for:**

- **Creating a regression model for `Sales ~ Any_Promo_Spend + Price_Decr_Spend`**
- **Interpreting the model results.**

## Import Libraries and Data

Let's load the `tidyverse` and `tidymodels` packages.

```{r}
# Load packages.
library(tidyverse)
library(tidymodels)
```

Import the `soup_data.csv`.

```{r}
soup_data <- read_csv("soup_data.csv")
```

## Model Estimation

In this case, the story has been defined for us. Kroger is specifically interested in whether their spend on promotions (`Any_Promo_Spend`) and discounts (`Price_Decr_Spend`) is driving their sales (`Sales`) in the soup category. Let's build a model using these variables.

```{r}
sales_model <- linear_reg() |>
  set_engine("lm") |>
  fit(Sales ~ Any_Promo_Spend + Price_Decr_Spend, data = soup_data)
```

## Model Interpretation

Let's examine the coefficients to see how spend on promotions and discounts might be affecting sales.

```{r}
sales_model |>
  tidy()
```

Based on the model, it looks like spend on promotions has a positive affect on sales, whereas discounts actually have a negative affect.
